Convective heat transport in stratified atmospheres at low and high Mach number

### 2016-10-11 tex/nusselt_paper.tex
fixes sign on viscous terms

We evolve the Fully Compressible Navier-Stokes equations,
which take the form:
\begin{align}
&\begin{aligned}
&\frac{D \ln\rho}{D t} = -\Div{\bm{u}}
	\label{eqn:continuity_eqn}
\end{aligned}\\
&\begin{aligned}
\frac{D\bm{u}}{D t}=
&-\grad T - T\grad\ln\rho + \bm{g} \\
&\,\,\,\,-\nu\Div{\lilstressT} - \lilstressT\cdot\grad\nu - \nu\lilstressT\cdot\grad\ln\rho
\label{eqn:momentum_eqn}
\end{aligned}\\
&\begin{aligned}
\frac{D T}{D t} = -&(\gamma-1)T\Div{\bm{u}} + \frac{1}{c_V}\left( \chi\grad^2 T + \grad T \cdot \grad\chi  \right. \\ \
&+ \chi\grad T \cdot\grad\ln\rho +\nu\left[\lilstressT\cdot\nabla\right]\cdot\bm{u}\left.\right) 
	\label{eqn:energy_eqn}
\end{aligned}
\end{align}
where $D/Dt \equiv \partial_t + \bm{u}\cdot\grad$ and the viscous stress tensor is defined as
\begin{equation}
\sigma_{ij} \equiv \left(\frac{\partial u_i}{\partial x_j} + \frac{\partial u_j}{\partial x_i} - \frac{2}{3}\delta_{ij}\Div{\bm{u}}\right).
	\label{eqn:stress_tensor}
\end{equation}

In such stratified systems, the total convective flux is
\begin{equation}
\bm{F}_{\text{conv}} \equiv \bm{F}_{\text{enth}} + \bm{F}_{\text{KE}} + \bm{F}_{\text{PE}} + \bm{F}_{\text{visc}},
\end{equation}
where $\bm{F}_{\text{enth}} \equiv \rho\bm{u}(c_V T + P/\rho)$ is the enthalpy flux, $\bm{F}_{\text{KE}} \equiv 
\rho|\bm{u}|^2\bm{u}$ is the kinetic energy flux, $\bm{F}_{\text{PE}} \equiv \rho\bm{u}\phi$ is the potential
energy flux (with $\phi \equiv -gz$), 
and $\bm{F}_{\text{visc}} \equiv -\rho\nu\bm{u}\cdot\lilstressT$ is the viscous flux.  Taking an inner product of
Eq. \ref{eqn:momentum_eqn} with $\bm{u}$ and adding it to 
Eq. \ref{eqn:energy_eqn}, the full energy equation in conservation form is retrieved,
\begin{equation}
\frac{\partial}{\partial t}\left(\rho\left[\frac{|\bm{u}|^2}{2} + c_V T + \phi\right]\right) +
\Div{\bm{F}_{\text{conv}} + \bm{F}_{\text{cond}}} = 0
	\label{eqn:energy_eqn_full}
\end{equation}
where $\bm{F}_{\text{cond}} = -\kappa \grad T$.  An understanding of the flux terms is essential to characterizing
the convective heat transport in our systems.

>>>>

We evolve the Fully Compressible Navier-Stokes equations,
which take the form:
\begin{align}
&\begin{aligned}
&\frac{D \ln\rho}{D t} = -\Div{\bm{u}}
	\label{eqn:continuity_eqn}
\end{aligned}\\
&\begin{aligned}
\frac{D\bm{u}}{D t}=
&-\grad T - T\grad\ln\rho + \bm{g} \\
&\,\,\,\,+\nu\Div{\lilstressT} + \lilstressT\cdot\grad\nu + \nu\lilstressT\cdot\grad\ln\rho
\label{eqn:momentum_eqn}
\end{aligned}\\
&\begin{aligned}
\frac{D T}{D t} = -&(\gamma-1)T\Div{\bm{u}} + \frac{1}{c_V}\left( \chi\grad^2 T + \grad T \cdot \grad\chi  \right. \\ \
&+ \chi\grad T \cdot\grad\ln\rho +\nu\left[\lilstressT\cdot\nabla\right]\cdot\bm{u}\left.\right) 
	\label{eqn:energy_eqn}
\end{aligned}
\end{align}
where $D/Dt \equiv \partial_t + \bm{u}\cdot\grad$ and the viscous stress tensor is defined as
\begin{equation}
\sigma_{ij} \equiv \left(\frac{\partial u_i}{\partial x_j} + \frac{\partial u_j}{\partial x_i} - \frac{2}{3}\delta_{ij}\Div{\bm{u}}\right).
	\label{eqn:stress_tensor}
\end{equation}

In such stratified systems, the total convective flux is
\begin{equation}
\bm{F}_{\text{conv}} \equiv \bm{F}_{\text{enth}} + \bm{F}_{\text{KE}} + \bm{F}_{\text{PE}} + \bm{F}_{\text{visc}},
\end{equation}
where $\bm{F}_{\text{enth}} \equiv \rho\bm{u}(c_V T + P/\rho)$ is the enthalpy flux, $\bm{F}_{\text{KE}} \equiv 
\rho|\bm{u}|^2\bm{u}/2$ is the kinetic energy flux, $\bm{F}_{\text{PE}} \equiv \rho\bm{u}\phi$ is the potential
energy flux (with $\phi \equiv -gz$), 
and $\bm{F}_{\text{visc}} \equiv -\rho\nu\bm{u}\cdot\lilstressT$ is the viscous flux.  Taking an inner product of
Eq. \ref{eqn:momentum_eqn} with $\bm{u}$ and adding it to 
Eq. \ref{eqn:energy_eqn}, the full energy equation in conservation form is retrieved,
\begin{equation}
\frac{\partial}{\partial t}\left(\rho\left[\frac{|\bm{u}|^2}{2} + c_V T + \phi\right]\right) +
\Div{\bm{F}_{\text{conv}} + \bm{F}_{\text{cond}}} = 0
	\label{eqn:energy_eqn_full}
\end{equation}
where $\bm{F}_{\text{cond}} = -\kappa \grad T$.  An understanding of the flux terms is essential to characterizing
the convective heat transport in our systems.
